AP/PA Tables ITHIM Global

### 2023-08-25 summary_tables.Rmd

# Script summarises mode splits, distances and durations travelled and looks at health outcomes (YLLs and deaths) for the different air pollution, injury and physical activity pathways but also by disease

@@

## Health outcomes - injury, air pollution and physical activity
# - one table for each city showing the change in total YLLs in the scenarios compared to the Baseline for each age group

# - one table for each city showing the change in YLLs per 100,000 people in the scenarios compared to the Baseline for each age group

# - one table for each city showing the change in YLLs per 100,000 people in the scenarios compared to the Baseline for each age and sex category

# - one table for each city showing the change in total YLLs due to changes in accident fatalities in the scenarios compared to the Baseline for each age group

# - one table for each city showing the change in total YLLs due to changes in physical activity levels in in the scenarios compared to the Baseline for each age group

# - one table for each city showing the change in total YLLs due to changes in air pollution (PM2.5) levels in in the scenarios compared to the Baseline for each age group

# - one table for each city showing the change in YLLs per 100,000 people due to changes in accident fatalities in the scenarios compared to the Baseline for each age group

# - one table for each city showing the change in YLLs per 100,000 people due to changes in physical activity levels in in the scenarios compared to the Baseline for each age group

# - one table for each city showing the change in YLLs per 100,000 people due to changes in air pollution (PM2.5) levels in in the scenarios compared to the Baseline for each age group

## Health outcomes - disease
# - one table for each city showing the change in deaths in the scenarios compared to the Baseline for each disease

# - one table for each city showing the change in deaths per 100,000 people in the scenarios compared to the Baseline for each disease

# - one table for each city showing the change in YLLs in the scenarios compared to the Baseline for each disease

# - one table for each city showing the change in YLLs per 100,000 people in the scenarios compared to the Baseline for each disease

@@

# - the ylls.csv file (results/multi_city/health_impacts/ylls.csv) gives the changes in YLLs for each age and sex category, for each age category per 100,000 people, and for each age and sex category per 100,000 people for each city, disease and scenario. It also shows the disease level, whether the disease is exasperated by changes in AP, PA or both, and the age and age and sex specific population levels. The results are for either AP and PA only if the diseases are affected by only AP or PA or the results for the combined AP and PA effects if the diseases are affected by both AP and PA.

# - the ylls_pathway.csv file (results/multi_city/health_impacts/ylls_pathway.csv) gives the changes in YLLs for each age and sex category, for each age category per 100,000 people, and for each age and sex category per 100,000 people for each city, disease and scenario. It also shows the disease level, whether the disease is exasperated by changes in AP or PA, and the age and age and sex specific population levels. The results are given for AP and PA independently even if a disease is affected by both pathways.

# - the deaths.csv file (results/multi_city/health_impacts/deaths.csv) gives the changes in deaths for each age and sex category, for each age category per 100,000 people, and for each age and sex category per 100,000 people for each city, disease and scenario. It also shows the disease level, whether the disease is exasperated by changes in AP, PA or both, and the age and age and sex specific population levels. The results are for either AP and PA only if the diseases are affected by only AP or PA or the results for the combined AP and PA effects if the diseases are affected by both AP and PA.

# - the deaths_pathway.csv file (results/multi_city/health_impacts/deaths_pathway.csv) gives the changes in deaths for each age and sex category, for each age category per 100,000 people, and for each age and sex category per 100,000 people for each city, disease and scenario. It also shows the disease level, whether the disease is exasperated by changes in AP or PA, and the age and age and sex specific population levels. The results are given for AP and PA independently even if a disease is affected by both pathways.

@@

# - set up helper function to re-format large numbers, re-name scenarios and format and print output tables

@@

# - create one table for each city showing the change in total YLLs in the scenarios compared to the Baseline for each age group

# - create one table for each city showing the change in YLLs per 100,000 people in the scenarios compared to the Baseline for each age group

# - create one table for each city showing the change in YLLs per 100,000 people in the scenarios compared to the Baseline for each age and sex category

# - create one table for each city showing the change in total YLLs due to changes in accident fatalities in the scenarios compared to the Baseline for each age group

# - create one table for each city showing the change in total YLLs due to changes in physical activity levels in in the scenarios compared to the Baseline for each age group

# - create one table for each city showing the change in total YLLs due to changes in air pollution (PM2.5) levels in in the scenarios compared to the Baseline for each age group

# - create one table for each city showing the change in YLLs per 100,000 people due to changes in accident fatalities in the scenarios compared to the Baseline for each age group

# - create one table for each city showing the change in YLLs per 100,000 people due to changes in physical activity levels in in the scenarios compared to the Baseline for each age group

# - create one table for each city showing the change in YLLs per 100,000 people due to changes in air pollution (PM2.5) levels in in the scenarios compared to the Baseline for each age group

# - create one table for each city showing the change in deaths in the scenarios compared to the Baseline for each disease

# - create one table for each city showing the change in deaths per 100,000 people in the scenarios compared to the Baseline for each disease

# - create one table for each city showing the change in YLLs in the scenarios compared to the Baseline for each disease

# - create one table for each city showing the change in YLLs per 100,000 people in the scenarios compared to the Baseline for each disease

# - create 4 individual .csv files in (results/multi_city/health_impacts/) for both death and YLLs considering the effect of AP and PA separately (*_pathway.csv) or together (*.csv). These files give the changes in YLLs / deaths for each age and sex category, for each age category per 100,000 people, and for each age and sex category per 100,000 people for each city, disease and scenario. They also show the disease level, whether the disease is exasperated by changes in AP, PA or both, and the age and age and sex specific population levels.

@@

```{r helper_functions, echo = F, message = F}
# Function to format numbers with million (M) and billion (B) suffixes
# Source: https://stackoverflow.com/questions/28159936/formatting-large-currency-or-dollar-values-to-millions-billions
comprss <- function(tx) { 
  div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
                      c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
  paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 2), 
        c("","K","M","B","T")[div] )
}

@@

# Get names of cities from the io object
cities <<- names(io)[!names(io) %in% 'scen_prop']
NSCEN <- nrow(io$scen_prop)

@@

```
# **1st option**
## Scenario definition 
<!-- Table displays highest propensity for each distance category, for a given mode. -->

@@

scen_prop <- round(io$scen_prop, round_to)

@@

orig_scen_names_updated <- unlist(lapply(rownames(scen_prop), FUN=get_qualified_scen_name))

@@

## Mode split for each scenario by city
City specific trip proportions by mode, for baseline and scenarios

@@

## Distance tables
City specific distance tables showing average distance in km travelled by each person by mode for all scenarios (incl Baseline)

```{r trip_dist = "asis"}
# find the average distance a person spends travelling on each mode per day

@@

  # update scenario names - cycle, car, bus
  colnames(td)[2:ncol(td)] <- c('Baseline', orig_scen_names_updated)

@@

  # write to .html
  print(kable(td, caption = paste("Distance table (km) per day for ", city, "( ", count_people, " ) per person")))
  cat("\n")

@@

  print(kable(td, caption = paste("Distance table (km) for ", city, "( ", count_people, " ) per person (people with trips ONLY)")))

@@

### Distance table showing average baseline distances in km travelled by each person by mode for all cities

@@

kable(trip_dist, caption = "Avg. baseline distance per person (km) per day across all cities")

@@

City specific distance tables for baseline and scenarios for the entire population with age range considered in the model

@@

  # find the total city level population considered in the model only
  #count_people <- round(sum(io[[city]]$demographic$population))

@@

# create baseline yearly distance table for all cities

@@

  print(kable(df, caption = paste("Model age population distance by mode per day for  ", city)))
}

@@

City specific duration tables for baseline and scenarios (per day in minutes)

```{r trip_dur = "asis"}
# create tables showing the average duration each person spends travelling per mode

@@

  # print to html
  print(kable(td, caption = paste("Duration table (mins) per day for model synthetic population for ", city, "( ", count_people, " ) per person (everyone)")))

@@

# find injury death column
#injury_col <- which(colnames(io[[1]]$outcomes$hb$deaths) == paste0(scen_names[2],'_deaths_inj'))

# find ap death columns
# ap_death_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('ap',as.character(x))))

@@

# find pa death columns
# pa_death_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('pa',as.character(x))))

@@

Change in YLLs per 100,000 people by age and sex category for each scenario compared to the reference scenario
```{r scen_prop = "asis"}
cat(' ')
cat(paste0('Reference scenario:  ', reference_scenario))

@@

YLLs per 100,000 people by age group by scenario - injury

@@

Change in total deaths compared to the reference scenario (for the city based on real population size) by scenario

@@

Change in deaths per 100,000 people by scenario in comparison to the reference scenario

@@

Change in total YLLs by disease compared to the reference scenario (for the city based on real population size, for ages considered within the ITHIM model)

@@

>>>>

# Script summarises mode splits, distances and durations travelled and looks at health outcomes (YLLs and deaths) for the different air pollution (AP), injury and physical activity (PA) pathways but also by disease

@@

## Health outcomes - injury, air pollution and physical activity
# - one table for each city showing the change in total YLLs for each of the scenarios compared to the reference scenario for each age group

# - one table for each city showing the change in YLLs per 100,000 people for each of the scenarios compared to the reference scenario for each age group

# - one table for each city showing the change in YLLs per 100,000 people for each of the scenarios compared to the reference scenario for each age and sex category

# - one table for each city showing the change in total YLLs due to changes in accident fatalities for each of the scenarios compared to the reference scenario for each age group

# - one table for each city showing the change in total YLLs due to changes in physical activity levels for each of the scenarios compared to the reference scenario for each age group

# - one table for each city showing the change in total YLLs due to changes in air pollution (PM2.5) levels for each of the scenarios compared to the reference scenario for each age group

# - one table for each city showing the change in YLLs per 100,000 people due to changes in accident fatalitiesfor each of the scenarios compared to the reference scenario for each age group

# - one table for each city showing the change in YLLs per 100,000 people due to changes in physical activity levelsfor each of the scenarios compared to the reference scenario for each age group

# - one table for each city showing the change in YLLs per 100,000 people due to changes in air pollution (PM2.5) levels for each of the scenarios compared to the reference scenario for each age group

## Health outcomes - disease
# - one table for each city showing the change in deaths for each of the scenarios compared to the reference scenario for each disease

# - one table for each city showing the change in deaths per 100,000 people for each of the scenarios compared to the reference scenario for each disease

# - one table for each city showing the change in YLLs for each of the scenarios compared to the reference scenario for each disease

# - one table for each city showing the change in YLLs per 100,000 people for each of the scenarios compared to the reference scenario for each disease

@@

# - the ylls.csv file (results/multi_city/health_impacts/ylls.csv) gives the changes in YLLs for each age and sex category, for each age category per 100,000 people, and for each age and sex category per 100,000 people for each city, disease and scenario compared to the reference scenario. It also shows the disease level, whether the disease is exasperated by changes in AP, PA or both, and the age, and age and sex specific population levels. The results are for either AP and PA only if the diseases are affected by only AP or PA or the results are for the combined AP and PA effects if the diseases are affected by both AP and PA.

# - the ylls_pathway.csv file (results/multi_city/health_impacts/ylls_pathway.csv) gives the changes in YLLs for each age and sex category, for each age category per 100,000 people, and for each age and sex category per 100,000 people for each city, disease and scenario compared to the reference scenario. It also shows the disease level, whether the disease is exasperated by changes in AP or PA, and the age, and age and sex specific population levels. The results are given for AP and PA independently even if a disease is affected by both pathways.

# - the deaths.csv file (results/multi_city/health_impacts/deaths.csv) gives the changes in deaths for each age and sex category, for each age category per 100,000 people, and for each age and sex category per 100,000 people for each city, disease and scenario compared to the reference scenario. It also shows the disease level, whether the disease is exasperated by changes in AP, PA or both, and the age, and age and sex specific population levels. The results are for either AP and PA only if the diseases are affected by only AP or PA or the results are for the combined AP and PA effects if the diseases are affected by both AP and PA.

# - the deaths_pathway.csv file (results/multi_city/health_impacts/deaths_pathway.csv) gives the changes in deaths for each age and sex category, for each age category per 100,000 people, and for each age and sex category per 100,000 people for each city, disease and scenario compared to the reference scenario. It also shows the disease level, whether the disease is exasperated by changes in AP or PA, and the age, and age and sex specific population levels. The results are given for AP and PA independently even if a disease is affected by both pathways.

@@

# - set up helper functions to re-format large numbers, re-name scenarios and format and print output tables

@@

# - create one table for each city showing the change in total YLLsfor each of the scenarios compared to the reference scenario  for each age group

# - create one table for each city showing the change in YLLs per 100,000 people for each of the scenarios compared to the reference scenario for each age group

# - create one table for each city showing the change in YLLs per 100,000 people for each of the scenarios compared to the reference scenario for each age and sex category

# - create one table for each city showing the change in total YLLs due to changes in accident fatalities for each of the scenarios compared to the reference scenario for each age group

# - create one table for each city showing the change in total YLLs due to changes in physical activity levels for each of the scenarios compared to the reference scenario for each age group

# - create one table for each city showing the change in total YLLs due to changes in air pollution (PM2.5) levels for each of the scenarios compared to the reference scenario for each age group

# - create one table for each city showing the change in YLLs per 100,000 people due to changes in accident fatalities for each of the scenarios compared to the reference scenario for each age group

# - create one table for each city showing the change in YLLs per 100,000 people due to changes in physical activity levels for each of the scenarios compared to the reference scenario for each age group

# - create one table for each city showing the change in YLLs per 100,000 people due to changes in air pollution (PM2.5) levelsfor each of the scenarios compared to the reference scenario for each age group

# - create one table for each city showing the change in deaths for each of the scenarios compared to the reference scenario for each disease

# - create one table for each city showing the change in deaths per 100,000 people for each of the scenarios compared to the reference scenario for each disease

# - create one table for each city showing the change in YLLs for each of the scenarios compared to the reference scenario for each disease

# - create one table for each city showing the change in YLLs per 100,000 people for each of the scenarios compared to the reference scenario for each disease

# - create 4 individual .csv files in 'results/multi_city/health_impacts/' for both death and YLLs considering the effect of AP and PA separately (*_pathway.csv) or together (*.csv). These files give the changes in YLLs or deaths for each age and sex category, for each age category per 100,000 people, and for each age and sex category per 100,000 people for each city, disease and scenario compared to the reference scenario. They also give the disease level, whether the disease is exasperated by changes in AP, PA or both, and the age and age and sex specific population levels.

@@

```{r helper_functions, echo = F, message = F}
# set up helper functions

# Function to format numbers with million (M) and billion (B) suffixes
# Source: https://stackoverflow.com/questions/28159936/formatting-large-currency-or-dollar-values-to-millions-billions
comprss <- function(tx) { 
  div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
                      c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
  paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 2), 
        c("","K","M","B","T")[div] )
}

@@

# Get names of cities from the io object
cities <<- names(io)[!names(io) %in% 'scen_prop']

# extract number of scenarios
NSCEN <- nrow(io$scen_prop)

@@

```
<!-- # **1st option** -->

## Distance categories

<!-- ## Scenario definition  -->
<!-- Table displays highest propensity for each distance category, for a given mode. -->

@@

# extract and update scenario names
scen_prop <- round(io$scen_prop, round_to)

@@

# rename scenarios
orig_scen_names_updated <- unlist(lapply(rownames(scen_prop), FUN=get_qualified_scen_name))

@@

## Mode split for each scenario by city

City specific trip proportions by mode, for baseline and scenarios

@@

## Distance tables
City specific distance tables showing average distance in km travelled by each person in the synthetic population by mode for all scenarios (incl Baseline)

```{r trip_dist = "asis"}
# find the average distance a person in the synthetic population spends travelling on each mode per day

@@

@@

  # write to .html
  print(kable(td, caption = paste("Distance table (km) per day for ", city, "( ", count_people, " ) per person in the synthetic population")))
  cat("\n")

@@

  print(kable(td, caption = paste("Distance table (km) for ", city, "( ", count_people, " ) per person in the synthetic population (people with trips ONLY)")))

@@

### Distance table showing average baseline distances in km travelled by each person in the synthetic population by mode for all cities

@@

kable(trip_dist, caption = "Avg. baseline distance (km) per person in the synthetic population per day across all cities")

@@

City specific distance tables for baseline and scenarios for the entire population with ages considered in the model

@@

@@

# create baseline yearly distance table for the entire population with ages considered in the model for all cities

@@

  print(kable(df, caption = paste("Total population distance with ages considered in model by mode per day for  ", city)))
}

@@

City specific duration tables for the synthetic population for baseline and scenarios (per day in minutes)

```{r trip_dur = "asis"}

# create tables showing the average duration each person in the synthetic population spends travelling per mode

@@

  # print to html
  print(kable(td, caption = paste("Duration table (mins) per day for synthetic population for ", city, "( ", count_people, " ) per person (everyone)")))

@@

@@

@@

Change in YLLs per 100,000 people by age and sex category for each scenario compared to the reference scenario

@@

<!-- YLLs per 100,000 people by age group by scenario - injury -->

@@

Change in total deaths compared to the reference scenario (for the city based on real population size but only for ages considered in the model) by scenario

@@

Change in deaths per 100,000 people (based on real population size but only for ages considered in the model) by scenario in comparison to the reference scenario

@@

Change in total YLLs by disease compared to the reference scenario (based on real population size, for ages considered within the ITHIM model)

@@

Change in total YLLs by disease compared to the reference scenario per 100,000 people (based on real population size, for ages considered within the ITHIM model)

### 2023-08-25 summary_tables_PA_AP.Rmd

# Script to summarise the PM2.5 exposure and levels, PM2.5 and CO2 concentrations and a physical activity levels

@@

# - one table for each city detailing the individual PM2.5 exposure levels incl the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the baseline scenario

@@

# - one table detailing the CO2 concentration levels for each scenario for all cities

@@

# - one table for each city detailing the individual PM2.5 exposure levels incl the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the baseline scenario. Table also contains CO2 concentrations for each scenario

@@

# - desc_stats.csv file (results/multi_city/AP/desc_stats.csv) containing the summary statistics of individual PM2.5 exposure levels, the total PM2.5 concentrations levels, the change in PM2.5 concentration levels compared to the baseline scenario and the total transport related CO2 emission concentrations for each scenario and city

@@

#   - summary_stats_PM2.5_CO2: summary statistics of individual PM2.5 exposure levels, the total PM2.5 concentrations levels, the change in PM2.5 concentration levels compared to the baseline scenario and the total transport related CO2 emission concentrations for each scenario and city

#### The script performs the following steps, assuming that ITHIM-GLOBAL module has been run and the ithim_objects object has been saved in "results/multi_city/io.rds":

@@

# - create one table for each city detailing the individual PM2.5 exposure levels incl. the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the baseline scenario

@@

# - create one table for each city detailing the individual PM2.5 exposure levels incl the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the baseline scenario. Table also contains CO2 concentrations for each scenario

@@

# scenario definition
scenario_name <- io[[city]]$ithim_run$scenarios_used
ref_scen <- io[[cities[1]]]$ithim_run$reference_scenario
reference_scenario <- get_qualified_scen_name(ref_scen)

compute_mode <- io[[city]]$ithim_run$compute_mode # constant parameters from the given parameters

@@

for(i in 1:length(parameter_names)){
  parameter_list[[parameter_names[i]]] <- list()
  parameter_index <- which(all_inputs$parameter==parameter_names[i]) 
  if(all_inputs[parameter_index,2]=='')  { 
    parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
      city_index <- which(colnames(all_inputs)==x)
      val <- all_inputs[parameter_index,city_index]
      ifelse(val%in%c('T','F'),val,ifelse(is.numeric(val), as.numeric(val), as.character(val)))
    })
    names(parameter_list[[parameter_names[i]]]) <- cities
  }else if(all_inputs[parameter_index,2]=='constant'){
    if (compute_mode != 'sample'){
      indices <- 0
      parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
        city_index <- which(colnames(all_inputs)==x)
        val <- all_inputs[parameter_index+indices,city_index]
        ifelse(val=='',0,as.numeric(val))
      })
    }
    if(compute_mode=='sample'){ # if sampling from distribution, check that distribution parameters exist
      parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
        indices <- 1:2
        city_index <- which(colnames(all_inputs)==x)  
        val <- all_inputs[parameter_index+indices,city_index] 
        if (val[1] == '' & val[2]==''){  # if no distribution parameters given in input file, read in constant value instead
          indices <-0
          city_index <- which(colnames(all_inputs)==x) 
          val <- all_inputs[parameter_index+indices,city_index]} 
        val <- as.numeric(val)
      })
    }
    names(parameter_list[[parameter_names[i]]]) <- cities
  }else{
    parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
      city_index <- which(colnames(all_inputs)==x)
      if(any(all_inputs[parameter_starts[i]:parameter_stops[i],city_index]!='')){
        sublist_indices <- which(all_inputs[parameter_starts[i]:parameter_stops[i],city_index]!='')
        thing <- as.list(as.numeric(c(all_inputs[parameter_starts[i]:parameter_stops[i],city_index])[sublist_indices]))
        names(thing) <- c(all_inputs[parameter_starts[i]:parameter_stops[i],2])[sublist_indices]
        thing
      }
    }
    )
    names(parameter_list[[parameter_names[i]]]) <- cities
  }
}

@@

for(i in 1:length(global_parameter_names)){
  global_parameter_list[[global_parameter_names[i]]] <- list()
  global_parameter_index <- which(all_global_inputs$parameter==global_parameter_names[i]) 
  if(all_global_inputs[global_parameter_index,2]=='')  {

@@

dist_cat <- unlist(strsplit(gsub(" ", "", dist_cat, fixed = TRUE), "\\,"))

@@

# for each city create a summary table of individual PM2.5 exposure levels giving the mean and the 5th, 50th and 95th percentile levels. Tables also show the PM2.5 concentration levels in the city for each scenario and the changes compared to the baseline scenario

@@

  n_col <- ncol(io[[cities[x]]]$outcomes$pm_conc_pp)
  # rename columns with updated scenario names
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - scen_length):n_col] <- new_scen_names

@@

  # add scenario specific PM2.5 concentration levels and the change in PM2.5 compared to the baseline
  summary$scenario_PM <- round(io[[cities[x]]]$outcomes$scenario_pm, digits=2)

@@

#city <- cities

@@

  # extract Co2 concentrations
  td <- round(colSums(io[[city]]$outcomes$co2_conc, na.rm = T), 1) %>% 
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', city)

@@

  # create the boxplots
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) +
    geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    labs(y = "Weekly mMET", x = "Scenarios")+  ylim(0, limit)
  print(y)

@@

# - one table for each city detailing the individual PM2.5 exposure levels incl the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the baseline scenario. Table also contains CO2 concentrations for each scenario

@@

  # add to io objects
  io[[cities[x]]]$summary_emission <- summary

  ## PM 2.5 table and plot

>>>>

# Script to summarise the PM2.5 personal exposure levels, PM2.5 and CO2 concentrations and physical activity levels

@@

# - one table for each city detailing the individual PM2.5 exposure levels including the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the reference scenario

@@

# - one table detailing the Baseline CO2 concentration levels for each scenario for all cities

@@

# - one table for each city detailing the individual PM2.5 exposure levels including the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the reference scenario. Table also contains CO2 concentrations for each scenario

@@

# - desc_stats.csv file (results/multi_city/AP/desc_stats.csv) containing the summary statistics of individual PM2.5 exposure levels, the total PM2.5 concentrations levels, the change in PM2.5 concentration levels compared to the reference scenario and the total transport related CO2 emission concentrations for each scenario and city

@@

#   - summary_stats_PM2.5_CO2: summary statistics of individual PM2.5 exposure levels, the total PM2.5 concentrations levels, the change in PM2.5 concentration levels compared to the reference scenario and the total transport related CO2 emission concentrations for each scenario and city

#### The script performs the following steps, assuming that the ITHIM-Global model has been run in CONSTANT mode and the ithim_objects object has been saved in "results/multi_city/io.rds":

@@

# - create one table for each city detailing the individual PM2.5 exposure levels incl. the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the reference scenario

@@

# - create one table for each city detailing the individual PM2.5 exposure levels including the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the reference scenario. Table also contains CO2 concentrations for each scenario

@@

# scenario and reference scenario definitions
scenario_name <- io[[city]]$ithim_run$scenarios_used
ref_scen <- io[[cities[1]]]$ithim_run$reference_scenario
reference_scenario <- get_qualified_scen_name(ref_scen)

compute_mode <- io[[city]]$ithim_run$compute_mode

@@

# extract local parameter information
for(i in 1:length(parameter_names)){
  parameter_list[[parameter_names[i]]] <- list()
  parameter_index <- which(all_inputs$parameter==parameter_names[i]) 
  if(all_inputs[parameter_index,2]=='')  { 
    parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
      city_index <- which(colnames(all_inputs)==x)
      val <- all_inputs[parameter_index,city_index]
      ifelse(val%in%c('T','F'),val,ifelse(is.numeric(val), as.numeric(val), as.character(val)))
    })
    names(parameter_list[[parameter_names[i]]]) <- cities
  }else if(all_inputs[parameter_index,2]=='constant'){
    if (compute_mode != 'sample'){
      indices <- 0
      parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
        city_index <- which(colnames(all_inputs)==x)
        val <- all_inputs[parameter_index+indices,city_index]
        ifelse(val=='',0,as.numeric(val))
      })
    }
    if(compute_mode=='sample'){ # if sampling from distribution, check that distribution parameters exist
      parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
        indices <- 1:2
        city_index <- which(colnames(all_inputs)==x)  
        val <- all_inputs[parameter_index+indices,city_index] 
        if (val[1] == '' & val[2]==''){  # if no distribution parameters given in input file, read in constant value instead
          indices <-0
          city_index <- which(colnames(all_inputs)==x) 
          val <- all_inputs[parameter_index+indices,city_index]} 
        val <- as.numeric(val)
      })
    }
    names(parameter_list[[parameter_names[i]]]) <- cities
  }else{
    parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
      city_index <- which(colnames(all_inputs)==x)
      if(any(all_inputs[parameter_starts[i]:parameter_stops[i],city_index]!='')){
        sublist_indices <- which(all_inputs[parameter_starts[i]:parameter_stops[i],city_index]!='')
        thing <- as.list(as.numeric(c(all_inputs[parameter_starts[i]:parameter_stops[i],city_index])[sublist_indices]))
        names(thing) <- c(all_inputs[parameter_starts[i]:parameter_stops[i],2])[sublist_indices]
        thing
      }
    }
    )
    names(parameter_list[[parameter_names[i]]]) <- cities
  }
}

@@

# extract global parameter information
for(i in 1:length(global_parameter_names)){
  global_parameter_list[[global_parameter_names[i]]] <- list()
  global_parameter_index <- which(all_global_inputs$parameter==global_parameter_names[i]) 
  if(all_global_inputs[global_parameter_index,2]=='')  {

@@

# get parameters into correct format
dist_cat <- unlist(strsplit(gsub(" ", "", dist_cat, fixed = TRUE), "\\,"))

@@

# for each city create a summary table of individual PM2.5 exposure levels giving the mean and the 5th, 50th and 95th percentile levels. Tables also show the PM2.5 concentration levels in the city for each scenario and the changes compared to the reference scenario

@@

  # rename columns with updated scenario names
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - scen_length):n_col] <- new_scen_names

@@

  # add scenario specific PM2.5 concentration levels 
  summary$scenario_PM <- round(io[[cities[x]]]$outcomes$scenario_pm, digits=2)

@@

@@

  # extract CO2 concentrations
  td <- round(colSums(io[[city]]$outcomes$co2_conc, na.rm = T), 1) %>% 
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', city)

@@

  # create the boxplots
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) +
    geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    labs(y = "Weekly mMET", x = "Scenarios")+  ylim(0, limit)

@@

# - one table for each city detailing the individual PM2.5 exposure levels incl the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the reference scenario. Table also contains CO2 concentrations for each scenario

@@

  # add to io object
  io[[cities[x]]]$summary_emission <- summary

  ## PM2.5 table and plot
